---
title: "Test distill datatable"
description: |
  testing distill details with datatable
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(DT)
# Learn more about creating websites with Distill at:
# https://rstudio.github.io/distill/website.html

```

## This is a minimum reproducible example

Here's [a discussion](https://community.rstudio.com/t/details-on-a-distill-site-works-on-chrome-but-not-firefox/134206/5) of the problem I've observed.


## demo trivial plot
```{r}
mtcars %>% ggplot(aes(x = mpg, y = wt)) +
  geom_point()
```
## demo datatable 

```{r}
mtcars %>% 
  select(mpg, wt) %>% 
  datatable()
```

## Different behavior with different browsers

Demo datatable inside a details section

<details>

- Everything works **great** with Chrome
- With Safari on a Mac, you can only see the data table if you press **Option-Command-i** -- two times!
- With Firefox on a Mac, you can only see the data table if you press **Option-Command-i** -- two times!
- With Firefox on a PC, you can only see the data table if you press **Control-Shift-i** -- two times!

```{r}
mtcars %>% 
  select(mpg, wt) %>% 
  datatable()
```

</details>
